Digital Analysis of Paintings

### 2014-05-07 paper.tex
Start on paper 15.

>>>>

One interesting use of stroke extraction is to animate Chinese paintings from
an original\cite{xu2006animating}. This is a complex procedure which involves
decomposing the painting based on brushstrokes, these brushstrokes can be
represented as vectorised elements and become easy to manipulate and therefore
animate.

To decompose the strokes the following method is proposed.

First, the image is over-segmented using a mean-shift algorithm, this is done
because colour is required to extract brushstrokes, but is not enough alone.
The over-segmentation stops regions spanning across multiple strokes, unless
the strokes themselves are overlapping.

The strokes are then extracted by merging these regions until they represent
the brushstroke. This requires some domain knowledge as naively merging these
regions may not represent the stroke accurately enough.

Two intuitions are used in this research: colour gradients are low along brush
strokes and strokes will match a library of strokes manually extracted from
other sources.
